Approximation as Differentiation notes

### 2025-03-03 notes/sec/grothendieck.tex
Tweaks.

\begin{enumerate}
\item $[X, Y]$ to be the object $(\Fam(C)(X,Y),[X, Y])$ in $\Fam(C)$ where we also write $[X,Y]$ for the
indexed family which maps every $(f: I \to J, g: X \to \reindex{Y}{f})$ in $\Fam(C)(X,Y)$ to
$\prod_{I}\reindex{Y}{f}$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) which sends any morphism $(f: I \times J
\to K, g: X \times Y \to \reindex{Z}{f}): X \times Y \to Z$ to the morphism $(f': I \to \Fam(C)(Y,Z), g': X
\to \reindex{[Y, Z]}{f'}): X \to [Y, Z]$ with:
\begin{itemize}
\item $f'(i) = (j \mapsto f(i, j): J \to K, j \mapsto g_{i,j} \comp \inj_{Y_j}: Y \to \reindex{Z}{j \mapsto
f(i, j)})$ where $\inj_{Y_j}: Y_j \to X_i \biprod Y_j$
\item $g' = \lambda_{\prod}(i \mapsto g_{i, j} \comp \inj_{X_i})$ where $\inj_{X_i}: X_i \to X_i \biprod
Y_j$ \todo{whence $j$?}
\end{itemize}
\item The family of morphisms $\eval_{X,Y} = (f', g'): [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $f': \Fam(C)(X,Y) \times I \to J = ((f, g), i) \mapsto f(i)$
\item $g': [X, Y] \times X \to \reindex{Y}{f} = ((f, g), i) \mapsto [{\eval_{\prod}}_i, g_i]$ where
${\eval_{\prod}}_i: \prod_I\reindex{Y}{f} \to Y_{f(i)}$
\end{itemize}
using $[-,-]$ to denote coproduct of morphisms.
\end{enumerate}
Then for any $f: X \times Y \to Z$ in $\Fam(C)$ we have \todo{(prove these)}:
\begin{enumerate}
\item The following diagram commutes:

>>>>

\begin{enumerate}
\item $[X, Y]$ to be the object $(\Fam(C)(X,Y),[X, Y])$ in $\Fam(C)$ where we also write $[X,Y]$ for the
indexed family which maps every $(f: I \to J, g: X \to \reindex{Y}{f}): X \to Y$ in $\Fam(C)$ to
$\prod_{I}\reindex{Y}{f}$.
\item The family of isomorphisms $\lambda_{X,Y,Z}$ (natural in $X$) which sends any morphism $(f: I \times J
\to K, g: X \times Y \to \reindex{Z}{f}): X \times Y \to Z$ to the morphism $(f': I \to \Fam(C)(Y,Z), g': X
\to \reindex{[Y, Z]}{f'}): X \to [Y, Z]$ with:
\begin{itemize}
\item $f'(i) = (j \mapsto f(i, j): J \to K, j \mapsto g_{i,j} \comp \inj_{Y_j}: Y \to \reindex{Z}{j \mapsto
f(i, j)})$ where $\inj_{Y_j}: Y_j \to X_i \biprod Y_j$
\item $g'(i) = \lambda_{\prod_{J}}(j \mapsto g_{i, j} \comp \inj_{X_i})$ where $\inj_{X_i}: X_i \to X_i \biprod
Y_j$ for every $j \in J$
\end{itemize}
\item The family of morphisms $\eval_{X,Y} = (f', g'): [X, Y] \times X \to Y$ in $\Fam(C)$ with
\begin{itemize}
\item $f': \Fam(C)(X,Y) \times I \to J = ((f, g), i) \mapsto f(i)$
\item $g': [X, Y] \times X \to \reindex{Y}{f} = ((f, g), i) \mapsto [{\eval_{\prod}}_i, g_i]$ where
${\eval_{\prod}}_i: \prod_I\reindex{Y}{f} \to Y_{f(i)}$
\end{itemize}
using $[-,-]$ to denote coproduct of morphisms.
\end{enumerate}
Then for any $f: X \times Y \to Z$ in $\Fam(C)$ we have \todo{(prove these)}:
\begin{enumerate}
\item The following diagram commutes:
